Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-18 ICML2019/main.tex
Tweak.
fix bugs

Unfolding the Hellinger distance formula, we get:\\
  \noindent \textbf{case: t is even}\\
  \begin{align*}
  & \Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 \\
  & = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

  \noindent \textbf{case: t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
  & \Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \\
  & =
  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
\qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

@@

Given $t$ with the same specific values ($1, 2, 3$ as above), we get the following accuracy equations on improved Laplace mechanism:
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\begin{align*}
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
&= 0.31606027941,\\
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\
&= 0.11627207896,\\
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}\\
&= 0.04277410743.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
\[
LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
\]
can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$
by applying the distance triangle property.

Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
\begin{align*}
&LS(\dataobs)\\
& = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{|\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
  &\qquad\qquad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))\}.
\end{align*}

>>>>

Unfolding the Hellinger distance formula, we get:\\
  \noindent \textbf{case: t is even}
  \begin{align*}
  &\Pr\left[
\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2}\\
&= 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot\prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
\end{aligned}
\right] \\
  &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
  \end{align*}
  \noindent \textbf{case: t is odd}
  let $t = 2 m + 1$
  \begin{align*}
  & \Pr\left[
	\begin{aligned}\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )^2} \\
  & =
  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
&\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  }\\ &\cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})} \end{aligned}
\right] \\
   &\qquad = \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})
  \end{align*}

@@

Given $t$ with the same specific values ($1, 2, 3$ as above), we get the following accuracy equations on improved Laplace mechanism:
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\begin{align*}
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
&= 0.31606027941,\\
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\
&= 0.11627207896,\\
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}\\
&= 0.04277410743.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
\[
LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
\]
can be reduced to $\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$
by applying the distance triangle property.

Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
\begin{align*}
LS(\dataobs)
& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
\left|~
\begin{aligned}
&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{aligned}
\right|\\
  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
\end{align*}
